---
title: "R Notebook"
output: html_notebook
---

LOAD LIBRARIES, DATA SET
```{r}
# Install packages
install.packages("arules")
install.packages("knitr")

# Load in libraries
library(tidyverse)
library(ggplot2)
library(lubridate)
library(skimr)
library(psych)
library(Hmisc)
library(corrplot)
library(naniar)
library(GGally)
library(janitor)
library(arules)
library(formattable)
library(knitr)

# Load in data set
countries <- read_csv("countries_clean.csv")

# Rename error in column name
countries %>% rename("veg_pop_2021" = "veg_pop_20201") -> countries

```

DESCRIPTIVE STATISTICS & HISTOGRAMS
```{r}
# Summaries of basic descriptives of numeric data
countries %>% psych::describe()

# Intentions - flexitarian, carbon emissions
hist(countries$yes_flex)
hist(countries$no_flex)

hist(countries$yes_reduce_carbon)
hist(countries$no_reduce_carbon)

# Behavior - meat consumption, veg population
hist(countries$meat_2020)
hist(countries$meat_2021)

hist(countries$veg_pop_2020)
hist(countries$veg_pop_2021)

# Expenditure on meat
hist(countries$expense_meat_2020)
hist(countries$expense_meat_2021)

```

COMPARISONS ACROSS YEARS
```{r}
# Bar charts - meat consumption
countries %>%
  select(
    meat_2020,
    meat_2021,
    processed_meat_2020,
    processed_meat_2021
  ) %>%
  summarise_all(mean, na.rm = T) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "average_value") %>%
  ggplot(aes(x = variable, y = average_value)) + geom_bar(stat = "identity")

# Bar charts - meat consumption
countries %>%
  select(
    veg_pop_2020,
    veg_pop_2021
  ) %>%
  summarise_all(mean, na.rm = T) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "average_value") %>%
  ggplot(aes(x = variable, y = average_value)) + geom_bar(stat = "identity")

# Bar charts - DPI, meat expenditure
countries %>%
  select(
    expense_meat_2020,
    expense_meat_2021,
    disposable_income_2020,
    disposable_income_2021
  ) %>%
  summarise_all(mean, na.rm = T) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "average_value") %>%
  ggplot(aes(x = variable, y = average_value)) + geom_bar(stat = "identity")

```

T-TESTS
```{r}
# Behavior - meat consumption, veg population
t.test(countries$meat_2020, countries$meat_2021)
t.test(countries$veg_pop_2020, countries$veg_pop_2021)
t.test(countries$expense_meat_2020, countries$expense_meat_2021)

```


DATA TRANSFORMATION - MEAT CONSUMPTION
```{r}
# Per inhabitant
## Meat consumption, processed meat consumption
countries %>%
  mutate(
    meat_2020 = meat_2020 / Population,
    meat_2021 = meat_2021 / Population,
    processed_meat_2020 = processed_meat_2020 / Population,
    processed_meat_2021 = processed_meat_2021 / Population
  ) -> countries


# Percentage increase from previous year
## Meat consumption
countries %>%
  mutate(
    meat_pct_change = ((meat_2021 - meat_2020) / meat_2020) * 100,
    processed_pct_change = ((processed_meat_2021 - processed_meat_2020) / processed_meat_2020) * 100,
    DPI_pct_change = ((disposable_income_2021 - disposable_income_2020) / disposable_income_2020) * 100,
    veg_pct_change = ((veg_pop_2021 - veg_pop_2020) / veg_pop_2020) * 100
  ) -> countries

```

DATA TRANSFORMATION - VEGETARIANS
```{r}
# Create new variables to represent percentage of population who are vegetarians
countries %>%
  mutate(
    veg_pct_pop_2020 = (veg_pop_2020 / Population) * 100,
    veg_pct_pop_2021 = (veg_pop_2021 / Population) * 100
  ) -> countries

# Create new variable to represent percentage change (2020-2021) in % of population who are vegetarians
countries %>%
  mutate(
    veg_pct_pop_change = ((veg_pct_pop_2021 - veg_pct_pop_2020) / veg_pct_pop_2020) * 100
  ) -> countries

```

DATA TRANSFORMATION - POPULATION
```{r}
# Transform population into thousands
countries %>%
  mutate(
    Population = Population / 1000
  ) -> countries

```

DATA TRANSFORMATION - HOFSTEDE
```{r}
# Transform all Hofstede variables into dummy (high, medium, low levels)
countries$IDV_class <- as.factor(ifelse(countries$Hofstede_IDV < 50, "Low",
                               ifelse(countries$Hofstede_IDV > 50, "High", NA)))

countries$UAI_class <- as.factor(ifelse(countries$Hofstede_UAI < 50, "Low",
                               ifelse(countries$Hofstede_UAI > 50, "High", NA)))

countries$LTO_class <- as.factor(ifelse(countries$Hofstede_LTO < 50, "Low",
                               ifelse(countries$Hofstede_LTO > 50, "High", NA)))

```

DATA TRANSFORMATION - GDP
```{r}
# Create a new variable to represent dummy categories of GDP 
countries %>%
  mutate(
    gdp_level = discretize(gdp_usd, breaks = 3, labels = c("Low", "Medium", "High"))
  ) -> countries

```

REFORMAT DATA SET COLUMNS & DELETE REMAINING UNECESSARY VARIABLES
```{r}
# Delete redundant and unnecessary variables
countries %>% select(-meat_2020, -meat_2021, -ValueSurvey_Attitudes,
                     -processed_meat_2020, -processed_meat_2021, -veg_pop_2020,
                     -veg_pop_2021, -veg_pct_change, -veg_pct_pop_2020, -veg_pct_pop_2021,
                     -disposable_income_2020, -disposable_income_2021) -> countries

countries %>% select(-expense_meat_2020, -expense_meat_2021, -no_flex, -no_reduce_carbon) -> countries

# Change column positioning
countries %>% relocate(IDV_class, UAI_class, LTO_class, .after = Hofstede_LTO) -> countries
countries %>% relocate(gdp_level, .after = gdp_usd) -> countries
countries %>% relocate(meat_replies, .after = yes_flex) -> countries
countries %>% relocate(emissions_replies, .after = yes_reduce_carbon) -> countries
```


DESCRIPTIVES
CORRELATIONS
PLOTS


DESCRIPTIVES TABLE
```{r}
# Summary descriptives
countries %>% psych::describe()

# Make table of summary statistics
# (population, gdp, flex, reduce carbon, meat change, processed change, DPI change, veg change)
## Mean, median, sd, min, max
countries %>%
  select(Population, gdp_usd, yes_flex, meat_pct_change,
         processed_pct_change, veg_pct_pop_change) %>%
  summarise_all(mean) -> stats_table

countries %>%
  select(Population, gdp_usd, yes_flex, meat_pct_change,
         processed_pct_change, veg_pct_pop_change) %>%
  summarise_all(median) -> stats_table_2

countries %>%
  select(Population, gdp_usd, yes_flex, meat_pct_change,
         processed_pct_change, veg_pct_pop_change) %>%
  summarise_all(sd) -> stats_table_3

countries %>%
  select(Population, gdp_usd, yes_flex, meat_pct_change,
         processed_pct_change, veg_pct_pop_change) %>%
  summarise_all(min) -> stats_table_4

countries %>%
  select(Population, gdp_usd, yes_flex, meat_pct_change,
         processed_pct_change, veg_pct_pop_change) %>%
  summarise_all(max) -> stats_table_5

# Combine all stats rows
bind_rows(stats_table, stats_table_2, stats_table_3, stats_table_4, stats_table_5) -> stats_table

# Reformat table
rownames(stats_table) <- c("Mean",
                           "Median",
                           "SD",
                           "Min",
                           "Max")

colnames(stats_table) <- c("Population",
                           "GDP",
                           "Flexitarian Respondents (% Total)",
                           "Meat Consumption % Change",
                           "Processed Meat Consumption % Change",
                           "Vegetarians % Change")

formattable(stats_table)

```

FREQUENCIES
```{r}
# GDP level frequency
countries %>% 
  tabyl(gdp_level) %>%
  adorn_pct_formatting(digits = 2) %>%
  adorn_totals()

# Hofstede measures frequencies
countries %>% 
  tabyl(IDV_class) %>%
  adorn_pct_formatting(digits = 2) -> test

countries %>% 
  tabyl(UAI_class) %>%
  adorn_pct_formatting(digits = 2)

countries %>% 
  tabyl(LTO_class) %>%
  adorn_pct_formatting(digits = 2)
  
  
```

HISTOGRAMS - GROUPING BY CATEGORICAL VARIABLES (GDP LEVEL BY DVS)
```{r}
# GDP level on flexitarians
countries %>%
  ggplot() + geom_histogram(aes(yes_flex), fill = "#1a6b89", bins = 20) +
  facet_wrap(gdp_level~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Flexitarian Respondents (%)",
    y = "Count (Countries)")

# GDP level on reducing carbon emissions
countries %>%
  ggplot() + geom_histogram(aes(yes_reduce_carbon), fill = "#1a6b89", bins = 20) +
  facet_wrap(gdp_level~., scales="free") +
  theme_classic(base_size = 20) +
  labs(
    x = "Carbion-Conscious Respondents (%)",
    y = "Count (Countries)")

# GDP level on meat consumption change
countries %>%
  ggplot() + geom_histogram(aes(meat_pct_change), fill = "#1a6b89", bins = 20) +
  facet_wrap(gdp_level~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Meat Consumption Change (%)",
    y = "Count (Countries)")

# GDP level on processed meat consumption change
countries %>%
  ggplot() + geom_histogram(aes(processed_pct_change), fill = "#1a6b89", bins = 20) +
  facet_wrap(gdp_level~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Processed Meat Consumption Change (%)",
    y = "Count (Countries)")

# GDP level on vegetarians change
countries %>%
  ggplot() + geom_histogram(aes(veg_pct_pop_change), fill = "#1a6b89", bins = 15) +
  facet_wrap(gdp_level~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Change in Vegetarian Population (%)",
    y = "Count (Countries)")
 
```

HISTOGRAMS - GROUPING BY CATEGORICAL VARIABLES (HOFSTEDE IDV BY DVS)
```{r}
# Hofstede IDV on flexitarians
countries %>%
  ggplot() + geom_histogram(aes(yes_flex), fill = "#198C57", bins = 25) +
  facet_wrap(Hofstede_IDV~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Flexitarian Respondents (%)",
    y = "Count (Countries)")

# Hofstede IDV on reducing carbon emissions
countries %>%
  ggplot() + geom_histogram(aes(yes_reduce_carbon), fill = "#198C57", bins = 25) +
  facet_wrap(Hofstede_IDV~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Carbion-Conscious Respondents (%)",
    y = "Count (Countries)")

# Hofstede IDV on meat consumption change
countries %>%
  ggplot() + geom_histogram(aes(meat_pct_change), fill = "#198C57", bins = 25) +
  facet_wrap(Hofstede_IDV~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Meat Consumption Change (%)",
    y = "Count (Countries)")

# Hofstede IDV on processed meat consumption change
countries %>%
  ggplot() + geom_histogram(aes(processed_pct_change), fill = "#198C57", bins = 30) +
  facet_wrap(Hofstede_IDV~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Processed Meat Consumption Change (%)",
    y = "Count (Countries)")

# Hofstede IDV on vegetarians change
countries %>%
  ggplot() + geom_histogram(aes(veg_pct_pop_change), fill = "#198C57", bins = 20) +
  facet_wrap(Hofstede_IDV~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Change in Vegetarian Population (%)",
    y = "Count (Countries)")

```

HISTOGRAMS - GROUPING BY CATEGORICAL VARIABLES (HOFSTEDE UAI BY DVS)
```{r}
# Hofstede UAI on flexitarians
countries %>%
  ggplot() + geom_histogram(aes(yes_flex), fill = "#DD6A60", bins = 25) +
  facet_wrap(Hofstede_UAI~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Flexitarian Respondents (%)",
    y = "Count (Countries)")

# Hofstede UAI on reducing carbon emissions
countries %>%
  ggplot() + geom_histogram(aes(yes_reduce_carbon), fill = "#DD6A60", bins = 25) +
  facet_wrap(Hofstede_UAI~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Carbion-Conscious Respondents (%)",
    y = "Count (Countries)")

# Hofstede UAI on meat consumption change
countries %>%
  ggplot() + geom_histogram(aes(meat_pct_change), fill = "#DD6A60", bins = 20) +
  facet_wrap(Hofstede_UAI~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Meat Consumption Change (%)",
    y = "Count (Countries)")

# Hofstede UAI on processed meat consumption change
countries %>%
  ggplot() + geom_histogram(aes(processed_pct_change), fill = "#DD6A60", bins = 25) +
  facet_wrap(Hofstede_UAI~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Processed Meat Consumption Change (%)",
    y = "Count (Countries)")

# Hofstede UAI on vegetarians change
countries %>%
  ggplot() + geom_histogram(aes(veg_pct_pop_change), fill = "#DD6A60", bins = 20) +
  facet_wrap(Hofstede_UAI~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Change in Vegetarian Population (%)",
    y = "Count (Countries)")

```

HISTOGRAMS - GROUPING BY CATEGORICAL VARIABLES (HOFSTEDE LTO BY DVS)
```{r}
# Hofstede LTO on flexitarians
countries %>%
  ggplot() + geom_histogram(aes(yes_flex), fill = "#B18D09", bins = 20) +
  facet_wrap(Hofstede_LTO~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Flexitarian Respondents (%)",
    y = "Count (Countries)")

# Hofstede LTO on reducing carbon emissions
countries %>%
  ggplot() + geom_histogram(aes(yes_reduce_carbon), fill = "#B18D09", bins = 25) +
  facet_wrap(Hofstede_LTO~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Carbion-Conscious Respondents (%)",
    y = "Count (Countries)")

# Hofstede LTO on meat consumption change
countries %>%
  ggplot() + geom_histogram(aes(meat_pct_change), fill = "#B18D09", bins = 20) +
  facet_wrap(Hofstede_LTO~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Meat Consumption Change (%)",
    y = "Count (Countries)")

# Hofstede LTO on processed meat consumption change
countries %>%
  ggplot() + geom_histogram(aes(processed_pct_change), fill = "#B18D09", bins = 25) +
  facet_wrap(Hofstede_LTO~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Processed Meat Consumption Change (%)",
    y = "Count (Countries)")

# Hofstede LTO on vegetarians change
countries %>%
  ggplot() + geom_histogram(aes(veg_pct_pop_change), fill = "#B18D09", bins = 25) +
  facet_wrap(Hofstede_LTO~., scales="free") +
  theme_classic(base_size = 18) +
  labs(
    x = "Change in Vegetarian Population (%)",
    y = "Count (Countries)")

```


PRELIM CHECK MULTICOLLINEARITY
```{r}
# Correlation IVs - GDP, flex
cor(countries$gdp_usd, countries$yes_flex)

# Correlation IVs - GDP, Hofstede IDV
cor(countries$gdp_usd, countries$Hofstede_IDV)

# Correlation IVs - GDP, Hofstede UAI
cor(countries$gdp_usd, countries$Hofstede_UAI)

# Correlation IVs - GDP, Hofstede LTO
cor(countries$gdp_usd, countries$Hofstede_LTO)

# Correlation IVs - flex, Hofstede IDV
cor(countries$yes_flex, countries$Hofstede_IDV)

# Correlation IVs - flex, Hofstede UAI
cor(countries$yes_flex, countries$Hofstede_UAI)

# Correlation IVs - flex, Hofstede LTO
cor(countries$yes_flex, countries$Hofstede_LTO)

# Correlation IVs - Hofstede IDV, Hofstede UAI
cor(countries$Hofstede_IDV, countries$Hofstede_UAI)

# Correlation IVs - Hofstede IDV, Hofstede LTO
cor(countries$Hofstede_IDV, countries$Hofstede_LTO)

# Correlation IVs - Hofstede UAI, Hofstede LTO
cor(countries$Hofstede_UAI, countries$Hofstede_LTO)

# Correlation IVs - DPI change, flex
cor(countries$DPI_pct_change, countries$yes_flex)

# Correlation IVs - DPI change, Hofstede IDV
cor(countries$DPI_pct_change, countries$Hofstede_IDV)

# Correlation IVs - DPI change, Hofstede UAI
cor(countries$DPI_pct_change, countries$Hofstede_UAI)

# Correlation IVs - DPI change, Hofstede LTO
cor(countries$DPI_pct_change, countries$Hofstede_LTO)

```

CHECK CORRELATIONS
```{r}
# Correlation matrix
countries %>%
  select(
    Hofstede_IDV,
    Hofstede_UAI,
    Hofstede_LTO,
    yes_flex,
    meat_pct_change,
    veg_pct_pop_change,
    processed_pct_change,
    Population,
    gdp_usd,
    yes_reduce_carbon) %>%
  as.matrix %>% 
  rcorr() -> corr

corrplot(corr$r, method = "shade", order = "alphabet", type = "lower", addCoef.col = TRUE, tl.srt = 45, tl.pos = "ld")
```


CHECK CORRELATIONS - Flexitarian as IV
```{r}
# flex - meat change
countries %>%
  ggplot() + geom_point(aes(x = yes_flex, y = meat_pct_change)) +
  stat_smooth(aes(x = yes_flex, y = meat_pct_change), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Flexitarian Respondents (%)",
    y = "Meat Consumption Change (%)"
  ) + theme_minimal(base_size = 16)

# flex - processed meat change
countries %>%
  ggplot() + geom_point(aes(x = yes_flex, y = processed_pct_change)) +
  stat_smooth(aes(x = yes_flex, y = processed_pct_change), method = "lm", se = FALSE, size = 1.5, color = "#486856") +
  labs(
    x = "Flexitarian Respondents (%)",
    y = "Processed Meat Consumption Change (%)"
  ) + theme_classic(base_size = 15)

# flex - vegetarian pop change
countries %>%
  ggplot() + geom_point(aes(x = yes_flex, y = veg_pct_pop_change)) +
  stat_smooth(aes(x = yes_flex, y = veg_pct_pop_change), method = "lm", se = FALSE, size = 1.5)


```

CHECK CORRELATIONS - DPI change as IV
```{r}
# DPI change - meat change
countries %>%
  ggplot() + geom_point(aes(x = DPI_pct_change, y = meat_pct_change)) +
  stat_smooth(aes(x = DPI_pct_change, y = meat_pct_change), method = "lm", se = FALSE, size = 1.5)

# DPI change - processed meat change
countries %>%
  ggplot() + geom_point(aes(x = DPI_pct_change, y = processed_pct_change)) +
  stat_smooth(aes(x = DPI_pct_change, y = processed_pct_change), method = "lm", se = FALSE, size = 1.5)

# DPI change - vegetarian pop change
countries %>%
  ggplot() + geom_point(aes(x = DPI_pct_change, y = veg_pct_pop_change)) +
  stat_smooth(aes(x = DPI_pct_change, y = veg_pct_pop_change), method = "lm", se = FALSE, size = 1.5)

```

CHECK CORRELATIONS - Hofstede IDV as IV
```{r}
# Hofstede IDV - meat change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_IDV, y = meat_pct_change)) +
  stat_smooth(aes(x = Hofstede_IDV, y = meat_pct_change), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Hofstede IDV Score",
    y = "Meat Consumption Change (%)"
  ) + theme_minimal(base_size = 16)

# Hofstede IDV - processed meat change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_IDV, y = processed_pct_change)) +
  stat_smooth(aes(x = Hofstede_IDV, y = processed_pct_change), method = "lm", se = FALSE, size = 1.5)

# Hofstede IDV - vegetarian pop change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_IDV, y = veg_pct_pop_change)) +
  stat_smooth(aes(x = Hofstede_IDV, y = veg_pct_pop_change), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Hofstede IDV Score",
    y = "Change in Vegetarian Population (%)"
  ) + theme_minimal(base_size = 16)

```

CHECK CORRELATIONS - Hofstede UAI as IV
```{r}
# Hofstede UAI - meat change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_UAI, y = meat_pct_change)) +
  stat_smooth(aes(x = Hofstede_UAI, y = meat_pct_change), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Hofstede UAI Score",
    y = "Meat Consumption Change (%)"
  ) + theme_minimal(base_size = 16)

# Hofstede UAI - processed meat change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_UAI, y = processed_pct_change)) +
  stat_smooth(aes(x = Hofstede_UAI, y = processed_pct_change), method = "lm", se = FALSE, size = 1.5)

# Hofstede UAI - vegetarian pop change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_UAI, y = veg_pct_pop_change)) +
  stat_smooth(aes(x = Hofstede_UAI, y = veg_pct_pop_change), method = "lm", se = FALSE, size = 1.5)

```

CHECK CORRELATIONS - Hofstede LTO as IV
```{r}
# Hofstede LTO - meat change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_LTO, y = meat_pct_change)) +
  stat_smooth(aes(x = Hofstede_LTO, y = meat_pct_change), method = "lm", se = FALSE, size = 1.5, color = "#69b3a2") +
  labs(
    x = "Hofstede LTO Score",
    y = "Meat Consumption Change (%)"
  ) + theme_minimal(base_size = 16)


# Hofstede LTO - processed meat change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_LTO, y = processed_pct_change)) +
  stat_smooth(aes(x = Hofstede_LTO, y = processed_pct_change), method = "lm", se = FALSE, size = 1.5) +
  labs(
    x = "Hofstede LTO Score",
    y = "Processed Meat Consumption Change (%)"
  ) + theme_classic(base_size = 18)

# Hofstede LTO - vegetarian pop change
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_LTO, y = veg_pct_pop_change)) +
  stat_smooth(aes(x = Hofstede_LTO, y = veg_pct_pop_change), method = "lm", se = FALSE, size = 1.5)

```

CHECK CORRELATIONS - GROUPED BY CATEGORIES
```{r}
# Hofstede IDV - meat change (grouped by GDP level)
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_IDV, y = meat_pct_change, color = gdp_level), size = 3) +
  labs(
    x = "Hofstede IDV Score",
    y = "Meat Consumption Change (%)"
  ) + theme_classic(base_size = 18)

# Hofstede LTO - meat change (grouped by GDP level)
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_LTO, y = meat_pct_change, color = gdp_level), size = 3) +
  labs(
    x = "Hofstede LTO Score",
    y = "Meat Consumption Change (%)"
  ) + theme_classic(base_size = 18)

# Hofstede LTO - processed meat change (grouped by GDP level)
countries %>%
  ggplot() + geom_point(aes(x = Hofstede_LTO, y = processed_pct_change, color = gdp_level), size = 3) +
  labs(
    x = "Hofstede LTO Score",
    y = "Processed Meat Consumption Change (%)"
  ) + theme_classic(base_size = 18)
```

SCATTERPLOT - FLEX ON MEAT (GROUPED BY LTO)
```{r}
ggplot(countries, aes(yes_flex, meat_pct_change, color = LTO_class)) +
  geom_point(aes(color = LTO_class)) +
  stat_smooth(aes(group = LTO_class), method = "lm") +
  labs(
    x = "Flexitarian Respondents (%)",
    y = "Meat Consumption Change (%)"
  ) + theme_minimal(base_size = 16)


```

EXPORT NEW CSV FILE (WITH NEW VARIABLES)
```{r}
write.csv(countries, "/Users/angelchang/Desktop/VU/Master/P4/Modeling/Week 3/Assignment/country_final.csv", row.names=FALSE)

```


